Test of Adaptable User Interfaces

### 2015-07-07 paper.tex
Add ideas for related Work part

% =============================================================================
\section{Related Work}
% =============================================================================
TODO

>>>>

% =============================================================================
\section{Related Work}
% =============================================================================
Automation of adaptive UI testing may be achieved by several means :
- using Finite State Machine-based modeling which suffers scaling problems [TODO: ref]
- creating an abstraction of the UI which is then tested in place of the UI itself [TODO: ref Sophie's paper]
- automated planning for hierarchical test case generation may be used which involves genetic algorithms [TODO: ref]
- using "capture and replay" method is rejected, as it would involve one capture per version [TODO: ref]
